\documentclass[a4paper]{MagicalCV}

% Removing page numbers
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}

% Change the geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Defining your colors
\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-purple}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

% start document
\begin{document}

% Last update time
% \lastupdated

% Title name

\namesection{\Huge NICOLAS BENJAMIN}{OCAMPO}{
{\color{VividPurple} \normalsize \faLink} \normalsize \hspace{0.2em} \href{https://nicolasbenjaminocampo.com}{nicolasbenjaminocampo.com} \hspace{0.8em}%\\[0.6em]
\email{\normal \href{mailto:nicolas-benjamin.ocampo@unice.fr}{nicolas-benjamin.ocampo@unice.fr}} \hspace{0.4em}
\linkedin{\normal \href{https://www.linkedin.com/in/nicolasbenjaminocampo/}{nicolasbenjaminocampo}}
\\[1em]}

\begin{minipage}[t]{0.36\textwidth} 

% Educationdoc
\cvsection{Education} 

\subsection{Ph.D. in Computer Science}
\descript{Université Côte d’Azur}
\cvevent{Jan 2022 - Present}{Nice, France} 
\vspace{\topsep} % Hacky fix for awkward extra vertical space
Research on detecting implicit and subtle abusive/hateful messages in social media. Develop detecting methods and counter-narratives for healthy debates and freedom of speech.
\sectionsep

\subsection{M.S. in Computer Science}
\descript{Universidad Nacional de Córdoba}
\cvevent{Jan 2020 - Dec 2021}{Córdoba, Argentina}
\textbf{Thesis title}: \href{https://rdu.unc.edu.ar/handle/11086/22979}{\textit{``Use of relaxed plans in heuristic grounding"}} in the \href{https://liisgroup.github.io/}{Logics, Interaction and Intelligent Systems (LIIS)} research group at \href{https://www.famaf.unc.edu.ar/}{FaMAF}.

\textbf{Achievements}: Diploma awarded with ``special mention" (GPA 9.59 over 10).
\sectionsep

\subsection{B.S. in Computer Science}
\descript{Universidad Nacional de Córdoba}
\cvevent{Jan 2017 - Dec 2019}{Córdoba, Argentina}

% Coursework
\cvsection{Doctoral Trainings}
\subsection{Presented Seminars}
\textit{``Détection subtile du langage abusif"} presented in My thesis in 180 seconds, Université Côte d’Azur.
\cvevent{Mar 29th, 2023}{Cannes, France} 
\sectionsep

\textit{``We Need Two Poke Flutes to Wake You Up'' an In-depth Analysis of Implicit and Subtle Hate Speech Messages"} presented in the 3IA PhD/Postdoc Seminars. \cvevent{Sep 2nd, 2022}{Sophia Antip., France}
\sectionsep

\textit{``Towards Subtle and Implicit Hate Speech Detection"} presented in the Franco-German Workshop.
\cvevent{Jun 14th-15th, 2022}{Paris, France}
\sectionsep

\subsection{Attended Summer Schools}
\textit{``Language Technologies: Deep Learning"} at Universidad del País Vasco. 
\cvevent{Jul 4th-8th, 2022}{San Sebastián, Spain}

% Skills
%\cvsection{Skills}

%\subsection{Programming}
%Python \textbullet{}   R \textbullet{} PHP \textbullet{} C/C++ \textbullet{} HTML/CSS  \textbullet{}
%JavaScript \textbullet{} SQL 
%\sectionsep
%\subsection{Miscellaneous}
%Shell \textbullet{} \LaTeX \textbullet{} Tableau \textbullet{} Microsoft Office \textbullet{} Firebase \textbullet{} Git
%\sectionsep

% Honors
\cvsection{Awards} 

\subsection{10 Jóvenes Sobresalientes}
\descript{Bolsa de Comercio de Córdoba}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\href{https://bolsacba.com.ar/certamen/ganadores.php}{\faLink} Selected as one of Córdoba, Argentina's top young people in 2022 for dedication to study and research.
\sectionsep

\subsection{Premio Universidad}
\descript{Universidad Nacional de Córdoba}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\href{https://www.unc.edu.ar/comunicaci\%C3\%B3n/premios-universidad-la-unc-distingui\%C3\%B3-las-personas-con-mejores-promedios-que-egresaron}{\faLink} Second-best GPA in 2021 that concluded their Bachelor's and Master's studies in the required time.

% Column two
\end{minipage} 
\hfill
\begin{minipage}[t]{0.60\textwidth} 

% Experience
\cvsection{Work Experience}

\runsubsection{Teaching} \\
\descript{Université Côte d’Azur}
\cvevent{Jan 2022 - Present}{Nice, France} 
\vspace{\topsep} % Hacky fix for awkward extra vertical space
Deliver lectures and labs at the Master's/post-graduate levels, teaching \textbf{64 hours per year} at 3IA Côte d’Azur and Digital Lab/Centrale Marseille.
\sectionsep

%\runsubsection{Teaching Assistant / Mentor} \\
\descript{Universidad Nacional de Córdoba - FaMAF}
\cvevent{Mar 2020 - Mar 2022}{Córdoba, Argentina} 
\vspace{\topsep} % Hacky fix for awkward extra vertical space
Teaching 6-month CS courses totaling \textbf{4 hours per week}, creating materials, leading online meetings, and providing chat support.

\textbf{Courses}: Programming paradigms, Algorithms and data structures I, Networks, Operating systems.
\sectionsep

%\runsubsection{Teaching Assistant} \\
\descript{Instituto Técnico Superior Córdoba}
\cvevent{Sep 2020 - May 2021}{Córdoba, Argentina} 
\vspace{\topsep} % Hacky fix for awkward extra vertical space
Assisted students in oral exam preparation, presentation skills practice, and assignment presentations totaling \textbf{15 hours per month}.

\textbf{Courses}: User Interface, Software Validation and Verification.
\sectionsep

\runsubsection{Software Development Intern} \\
\descript{SimTLix (now intive)}
\cvevent{Oct 2021 - Dec 2021}{Córdoba, Argentina} 
\vspace{\topsep} % Hacky fix for awkward extra vertical space
3-month internship enhancing machine learning models for shoulder scan segmentation to assist doctors in prosthesis treatment.
%\cvsection{Internships} \\

% Publications
% Competitions
\cvsection{Participation in Scientific Activities}

\runsubsection{Reviewing activities for international top NLP and AI conferences} \\
\descript{}
%\cvevent{Apr 2022 - May 2022}{Sophia Antipolis, France} 
\vspace{\topsep} % Hacky fix for awkward extra vertical space
Reviewer in ECAI2023, EACL2023, CMNA2022, and ArgMining2022.
\sectionsep

\runsubsection{Journée Natural Language Argumentation Workshop Organizer} \\
\descript{Université Cote D'azur}
\cvevent{Nov 27th, 2023}{Sophia Antipolis, France}
\vspace{\topsep}
Organized and assisted in the Natural Language Argumentation Workshop, managing keynote sessions and overseeing administrative tasks.
\sectionsep

\runsubsection{Student Volunteer} \\
\descript{EACL 2023 Conference}
\cvevent{May 2nd-6th, 2023}{Dubrovnik, Croatia} 
\vspace{\topsep}
Volunteered at EACL 2023, assisting with in-person conference events and plenary sessions.
\sectionsep

\runsubsection{MOMI Workshop Organizer} \\
\descript{Inria Sophia Antipolis Méditerranée}
\cvevent{Apr 2022 - May 2022}{Sophia Antipolis, France} 
\vspace{\topsep} % Hacky fix for awkward extra vertical space
Organized MOMI 2022 workshop, managing website updates, speaker coordination, catering, registration, and overall event coordination.
\sectionsep
\end{minipage}

\newpage

\begin{minipage}[t]{1\textwidth} 
\cvsection{Publications}

\subsection{Unmasking the Hidden Meaning: Bridging Implicit and Explicit Hate Speech Embedding Representations}
\cvevent{Dec 2023}{Singapore}
N.B. Ocampo, E. Cabrio, and S. Villata \\
\href{https://aclanthology.org/2023.findings-emnlp.441/}{\faLink} Findings of the Association for Computational Linguistics (EMNLP 2023). \\ \textbf{Conference CORE Rank: A}.
\sectionsep

\subsection{Playing the Part of the Sharp Bully: Generating Adversarial Examples for Implicit Hate Speech Detection}
\cvevent{Jul 2023}{Toronto, Canada}
N.B. Ocampo, E. Cabrio, and S. Villata \\
\href{https://aclanthology.org/2023.findings-acl.173}{\faLink} Findings of the Association for Computational Linguistics (ACL 2023). \\ \textbf{Conference CORE Rank: A*}.
\sectionsep

\subsection{An In-depth Analysis of Implicit and Subtle Hate Speech Messages}
\cvevent{May 2023}{Dubrovnik, Croatia}
N.B. Ocampo, E. Sviridova, E. Cabrio, and S. Villata \\
\href{https://aclanthology.org/2023.eacl-main.147}{\faLink} Proceedings of the 17th Conference of the European Chapter of the Association for Computational Linguistics (EACL 2023). \\ \textbf{Conference CORE Rank: A}.

\end{minipage}

\end{document}  